---
title: "Opponents and Supporters of Marijuana Legalization"
subtitle: "Supporters and Opponents of Marijuana Legalization"
author: 
  - Zhongyu Huang
thanks: "Code and data are available at: https://github.com/zhongyuhuang/GSS_Analysis.git"
date: "`r format(Sys.time(), '%19 %3 %2022')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
# read the prepared data (stored in outputs/data/prepared_gss.csv)
f <- file.choose()
data <- read.csv(f)
```

# Introduction

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point). 



# Data

## The dataset

The data used here is obtained and merged based on the 2021 U.S General Social Survey. Our data set stores responses of 4032 participants who answered a GSS questionnaire from December 2020 to May 2021. We recode and create the following nine variables of interest that is used in our analysis:

- year: indicates the year for the respondent.
- Gender: indicates the gender of the respondent (female, male, transgender, none of these).
- age: indicates age of the respondent.
- Degree: respondent's degree (less than high school, high school, associate/junior college, bachelors, graduate).
- Race: indicates the race that the respondent considers her/himself (white, black, American indian or alaska native, Asian Indian, Chinese, Filipino, Japanese, Korean, Vietnamese, Other Asian, Native hawaiian, Guamanian or chamorro, Samoan, Other pacifis islander, Some other race, Hispanic).
- Party: indicates how do respondents usually think of themselves as a Republican,Democrat, or Independent (strong democrat, not very strong democrat, independent close to democrat, independent(neither or no response), independent close to republican, not very stong republican, strong republican).
- LegalVSIllegal: indicates whether respondents think the use of marijuana should be made legal or not (should be legal, should not be legal).
- Spend: indicates how do respondents think of the government's spend on dealing with drug addiction (too little, about right, too much).


## The Survey and its methodology

The General Social Survey (GSS) in the U.S is a national-wide survey that studies any trends of attitudes or opinions on American society. Its questionnaire covers lots of topics such as crime, civil liberties, morality and so on. Respondents are required be to be 18 or older who live in the United States at the time of interviewing.

During the COVID-19 pandemic, the GSS had changed its methodology from in-person interview to the push-to-web method. While the option of interviewing on phone remains available, participants can also obtain the survey through the web link that had been mailed to their houses. Different from in-person data collecting, the web survey provides the "skip" option when respondents are not willing to answer specific questions.    

## weakness and strength of the survey

Strength:

-


Weakness:

- The sample size of 4,032 completes of this survey might not be large enough to be served as a national-wide survey that claimed by GSS.
- Although the push-to-web methodology ensure the safety of both the interviewers and respondents, such a method might unintentionally set restrictions on respondents. For example, individuals are required to have some basic knowledge of computers.
- It is harder for web survey to achieve accurate information from respondents compared to the in-person interview. It is uncertain that who is really answering the questionnaire.
- It might be more incentive for participants give random or false responds during the web survey compared to the in-person method.



Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE, fig.height=5, fig.width=5}
ggplot(data, aes(x=Gender)) + geom_bar() +  labs(x='Gender')
ggplot(data, aes(x=Spend)) + geom_bar() +  labs(x='Spend')
ggplot(data, aes(x=LegalVSIllegal)) + geom_bar() +  labs(x='Legal or not ')
ggplot(data, aes(x=Party)) + geom_bar() +  labs(x='Party')
mosaicplot(LegalVSIllegal~Gender,data=data)
mosaicplot(LegalVSIllegal~Party,data=data)
mosaicplot(Spend~Gender,data=data)
mosaicplot(LegalVSIllegal~Degree,data=data)
ggplot(data, aes(x=LegalVSIllegal, y=age)) +
  geom_boxplot(fill='steelblue')
```

Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?

```

Talk way more about it. 



# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful. 

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}
survey link:

## Preamble:

purpose of the survey

## Questions


# Additional details


\newpage


# References


