---
title: "Opponents and Supporters of Marijuana Legalization"
subtitle: "Supporters and Opponents of Marijuana Legalization"
author: 
  - Zhongyu Huang
thanks: "Code and data are available at: https://github.com/zhongyuhuang/GSS_Analysis.git"
date: "`r format(Sys.time(), '%19 %3 %2022')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
# read the prepared data (stored in outputs/data/prepared_gss.csv)
f <- file.choose()
data <- read.csv(f)
```

# Introduction

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point). 



# Data

The data used here is obtained and merged based on the 2021 U.S General Social Survey. Our data set stores responses of 4032 participants who answered a GSS questionnaire from December 2020 to May 2021. We recode and create the following nine variables of interest that is used in our analysis:

- year: indicates the year for the respondent.
- Gender: indicates the gender of the respondent (female, male, transgender, none of these).
- age: indicates age of the respondent.
- Degree: respondent's degree (less than high school, high school, associate/junior college, bachelors, graduate).
- Race: indicates the race that the respondent considers her/himself (white, black, American indian or alaska native, Asian Indian, Chinese, Filipino, Japanese, Korean, Vietnamese, Other Asian, Native hawaiian, Guamanian or chamorro, Samoan, Other pacifis islander, Some other race, Hispanic).
- Party: indicates how do respondents usually think of themselves as a Republican,Democrat, or Independent (strong democrat, not very strong democrat, independent close to democrat, independent(neither or no response), independent close to republican, not very stong republican, strong republican).
- LegalVSIllegal: indicates whether respondents think the use of marijuana should be made legal or not (should be legal, should not be legal).
- Spend: indicates how do respondents think of the government's spend on dealing with drug addiction (too little, about right, too much).


## Survey's methodology

## weakness and strength of the survey

Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE, fig.height=5, fig.width=5}
ggplot(data, aes(x=Gender)) + geom_bar() +  labs(x='Gender')
ggplot(data, aes(x=Spend)) + geom_bar() +  labs(x='Spend')
ggplot(data, aes(x=LegalVSIllegal)) + geom_bar() +  labs(x='Legal or not ')
ggplot(data, aes(x=Party)) + geom_bar() +  labs(x='Party')
mosaicplot(LegalVSIllegal~Gender,data=data)
mosaicplot(LegalVSIllegal~Party,data=data)
mosaicplot(Spend~Gender,data=data)
mosaicplot(LegalVSIllegal~Degree,data=data)
ggplot(data, aes(x=LegalVSIllegal, y=age)) +
  geom_boxplot(fill='steelblue')
```

Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?

```

Talk way more about it. 



# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful. 

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}
survey link:

## Preamble:

purpose of the survey

## Questions


# Additional details


\newpage


# References


