---
title: "Opponents and Supporters of Marijuana Legalization"
subtitle: "Supporters and Opponents of Marijuana Legalization"
author: 
  - Zhongyu Huang
thanks: "Code and data are available at: https://github.com/zhongyuhuang/GSS_Analysis.git"
date: "`r format(Sys.time(), '%19 %3 %2022')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
#install.packages('gridExtra')
library(gridExtra)
library(ggplot2)
# read the prepared data (stored in outputs/data/prepared_gss.csv)
f <- file.choose()
data <- read.csv(f)
```

# Introduction

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point). 



# Data

## The dataset

The data used here is obtained and merged based on the 2021 U.S General Social Survey. Our data set stores responses of 4032 participants who answered a GSS questionnaire from December 2020 to May 2021. We recode and create the following nine variables of interest that is used in our analysis:

- year: indicates the year for the respondent.
- Gender: indicates the gender of the respondent (female, male, transgender, none of these).
- age: indicates age of the respondent.
- Degree: respondent's degree (less than high school, high school, associate/junior college, bachelors, graduate).
- Race: indicates the race that the respondent considers her/himself (white, black, American indian or alaska native, Asian Indian, Chinese, Filipino, Japanese, Korean, Vietnamese, Other Asian, Native hawaiian, Guamanian or chamorro, Samoan, Other pacifis islander, Some other race, Hispanic).
- Party: indicates how do respondents usually think of themselves as a Republican,Democrat, or Independent (strong democrat, not very strong democrat, independent close to democrat, independent(neither or no response), independent close to republican, not very stong republican, strong republican).
- LegalVSIllegal: indicates whether respondents think the use of marijuana should be made legal or not (should be legal, should not be legal).
- Spend: indicates how do respondents think of the government's spend on dealing with drug addiction (too little, about right, too much).


## The Survey and its methodology

The General Social Survey (GSS) in the U.S is a national-wide survey that studies any trends of attitudes or opinions on American society [@GSS]. Its questionnaire covers lots of topics such as crime, civil liberties, morality and so on. Respondents are required be to be 18 or older who live in the United States at the time of interviewing. They are sampled based on address.

During the COVID-19 pandemic, the GSS had changed its methodology from in-person interview to the push-to-web method. While the option of interviewing on phone remains available, participants can also obtain the survey through the web link that had been mailed to their houses. Different from in-person data collecting, the self-administered questionnaire based on web provides the "skip" option when respondents are not willing to answer specific questions. Initially, options like "No answer" or "Don't know" are not included in the in-person interview. But the interviewer can make a record when respondents do not want to answer specific questions.   

## Weakness and strength of the survey and the questionnaire

Strength:

- The survey covers wide range of topics which can provides informative trends of opinions or behaviors on the society.
- Methods used in designing the survey enabled objectivity.
- It is quick to gather large amount of information through questionnaires.
- The transformation from in-person interview to web survey provides Convenience and safety during the pandemic. 


Weakness:

- The sample size of 4,032 completes of this survey might not be large enough to be served as a national-wide survey that claimed by GSS.
- Although the push-to-web methodology ensure the safety of both the interviewers and respondents, such a method might unintentionally set restrictions on respondents. For example, individuals are required to have some basic knowledge of computers.
- It is harder for web survey to achieve accurate information from respondents compared to the in-person interview. It is uncertain that who is really answering the questionnaire.
- It might be more incentive for participants give random or false responds during the web survey compared to the in-person method.
- Length of the questionnaire might be too long for participant to answer patiently.
- Changes in response can not be tracked.



# Results

The histograms below have shown the composition of the respondents. (Figure \@ref(fig:characteristics)). Generation X (35-50) and the silent (70-87) who identify themselves as white make up the largest portion of the respondents. Half of the participants are female. If we view them according to their favor of political party, we can see most of them think themselves as independent or strong democrat. 


```{r characteristics, fig.cap="visualization of characteristics of respondents", echo = FALSE, fig.height=10, fig.width=10, warning=FALSE}
#make bar plot of gender
p1<- ggplot(data, aes(x=Gender)) + geom_bar() +  labs(x='Gender')
#make bar plot of age
p2<- ggplot(data, aes(x=age)) +geom_bar()
#make bar plot of race
p3<-ggplot(data, aes(x=Race)) + geom_bar() +  labs(x='Degree') +
  theme(axis.text.x = element_text(angle = 90))
#make bar plot of party
p4<-ggplot(data, aes(x=Party)) + geom_bar() + labs(x='Party')+ theme(axis.text.x = element_text(angle = 90))
#arrange four plots
grid.arrange(p1,p2,p3,p4)
```


The majority of responses regarding to whether the marijuana should be legal or not fall on not applicable(Figure \@ref(fig:LegalVSIllegal)). Despite that, the number of individuals that support the legalization of marijuana is approximately 3.5 times larger than those who disagree of the legalization. The majority of the supporters have these characteristics: female, strong democrat, obtain high school degree, at a younger age(approximately 35). The majority of the opponents have these characteristics: female,independent, obtain high school degree, at a relatively higher age(approximately 65)(Figure \@ref(fig:m)). 


```{r LegalVSIllegal, fig.cap="Opinions on legalization of marijuana", echo = FALSE, fig.height=3, fig.width=5, warning=FALSE}
# make bar plot of LegalVSIllegal
ggplot(data=data, aes(x=LegalVSIllegal)) + geom_bar() +  labs(x='Opinions on legalization of marijuana')
```


```{r m, fig.cap="characteristics of majorities", echo = FALSE, fig.height=5, fig.width=10, warning=FALSE}

#make bar plot of gender group by LegalVSIllegal
ggplot(data, aes(x=Gender)) + geom_bar() +  labs(x='Gender')+ facet_wrap(~LegalVSIllegal)
#make bar plot of race group by LegalVSIllegal
ggplot(data, aes(x=Race)) + geom_bar() +  labs(x='Race')+ facet_wrap(~LegalVSIllegal)+ theme(axis.text.x = element_text(angle = 90))
#make bar plot of degree group by LegalVSIllegal
ggplot(data, aes(x=Degree)) + geom_bar() +  labs(x='Degree')+ facet_wrap(~LegalVSIllegal)+ theme(axis.text.x = element_text(angle = 90))
#make bar plot of age group by LegalVSIllegal
ggplot(data, aes(x=age)) + geom_bar() +  labs(x='Age')+ facet_wrap(~LegalVSIllegal)

```


# Discussion

## Significant different in opinion on marijuana legalization by favor of political parties

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Significant different in opinion on marijuana legalization by age group

## The spend on dealing with drug addiction

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}
survey link:

## Preamble:

purpose of the survey

## Questions


# Additional details


\newpage


# References


